\begin{titlepage}
    \centering
    {\LARGE Western University\par}
    {\Large Department of Economics\par}
    \vspace{1cm}
    {\large $course-name$ \par
    $course-code$ \par
    $title$ \par
    Exam Version: $exam-version$ \par}
    \vspace{1cm}
    Instructor: $author$ \hfill Date:\enspace\rule{4cm}{0.4pt}\par
    \vspace{1cm}
    \raggedleft
    \makebox[\textwidth]{Name:\enspace\hrulefill\enspace Student No.:\enspace\rule{4cm}{0.4pt}}
    \vfill
    {\centering 
        {\bf Instructions \par}
    }
    \raggedleft
    % \small
    \begin{itemize}
        \item You will have 90 minutes to complete the exam.
        \item The exam contains 20 multiple choice questions and 2 short answer questions. To answer a multiple choice question fill in the bubble in the bubble sheet page. To answer a short-answer question write down your answer in the space provided.
        \item Record your name, student number, and exam version on the bubble sheet.
        \item In the short answer questions, please make sure that you clearly label all graphs and you explain the meaning of your results to get the full marks.
        \item You may have pencils, erasers, your student card, and a non-graphing non-programmable calculator out of its case on your desk. All other items including watches, and cell-phones must be left in your bag at the front of the examination room.
        \item Please ensure that all electronic devices (cell phones, laptops, tablets, smart watches etc.) are turned off before storing them in your bag at the front of the examination room.  Any internet-capable device found at your desk or on you during the exam may be viewed as an attempt to cheat, and academic offense procedures will ensue.
        \item When you have finished, please hand in all exam materials (i.e., bubble sheet, exam questions, work booklets).
    \end{itemize}
    \centering GOOD LUCK!
\end{titlepage}
\newpage

% \begin{center}
%     \fbox{\fbox{\parbox{5.5in}{\centering
%           Answer the questions in the spaces provided on the
%           question sheets.  If you run out of room for an answer,
%           continue on the back of the page.}}}
% \end{center}
% \vspace{0.1in}
% \makebox[\textwidth]{Name and section:\enspace\hrulefill}
% \vspace{0.2in}
% \makebox[\textwidth]{Instructor’s name:\enspace\hrulefill}